Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-10 paper.qmd
Added Figure 11 with a box

tsne_gau <- tsne_gau_scaled |>
  ggplot(aes(x = tSNE1,
             y = tSNE2)) +
  geom_point(alpha=0.3, color = "#000000")

>>>>

tsne_gau <- tsne_gau_scaled |>
  ggplot(aes(x = tSNE1,
             y = tSNE2)) +
  geom_point(alpha=0.3, color = "#000000") +
  geom_rect(aes(xmin = -0.05, xmax = 0.35, ymin = 0.28, ymax = 0.6),
               fill = "transparent", color = "red", linewidth = 0.8)
